%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Graduate Research Assistant} % Job title
    {Coon Lab} % Organization
    {Madison, WI} % Location
    {05/2016--present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed, optimized, and implemented state-of-the-art mass spectrometry-based proteomic experiments to inform upon a range of \\biological studies.}
      \end{cvitems}
    }
    
      \cventry
    {Chemist I} % Job title
    {Warp Drive Bio} % Organization
    {Cambridge, MA} % Location
    {10/2012--5/2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Purified and characterized novel, medicinal natural products from complex, cellular matrices.}
        \item {Became versed in chromatographic techniques, instrument repair, and NMR structure elucidation.}
      \end{cvitems}
    }
    
      \cventry
    {Organic Chemist} % Job title
    {Johnson Matthey Pharma Services} % Organization
    {Devens, MA} % Location
    {02/2012--5/2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Produced synthetic GMP material; working on scales from milligrams to kilograms.}
        \item {Optimized future GMP campaigns at the bench-top.}
      \end{cvitems}
    }

      \cventry
    {Tutor} % Job title
    {Cardinal Academics} % Organization
    {Los Angeles, CA} % Location
    {01/2011--01/2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Provided tutoring for students in math, science, and SAT preparation.}
      \end{cvitems}
    }
    
      \cventry
    {Scientific Associate II} % Job title
    {Vertex Pharmaceuticals} % Organization
    {Cambridge, MA} % Location
    {06/2010--10/2010} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Performed analytical and preparative supercritical fluid chromatography to assist in the projects of Chemical Development.}
        \item {Trained on cGMP SOPs for the quality production of drug product.}
      \end{cvitems}
    }
    
      \cventry
    {Undergradute Research Fellow} % Job title
    {Bierbach Lab} % Organization
    {Winston-Salem, NC} % Location
    {2008-2010} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Synthesized cisplatin derivatives with Pf. Ulrich Bierbach for the structure-activity relationship analysis in the targeted treatment of non-small cell lung cancer.}
        \item {Developed new synthetic methodologies to produce amidine derivatives using metal-mediated catalysis.}
      \end{cvitems}
    }      
    
      \cventry
    {Undergraduate Tutoring Service} % Job title
    {Wake Forest University} % Organization
    {Winston-Salem, NC} % Location
    {01/2008--05/2010} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Provided peer tutoring to fellow Wake Forest and local high school students.}
      \end{cvitems}
    }    
    


%---------------------------------------------------------

%---------------------------------------------------------
\end{cventries}
